
\chapter{个人简历、在读期间发表的学术论文与取得的研究成果}

\textbf{个人简历}

1988年3月31日生于山东省滕州市。

2003年9月考入中国科学技术大学少年班，2007年7月本科毕业并获得理学学士学位。

2007年9月进入中国科学技术大学微尺度国家实验室直接攻博至今。


\textbf{已发表论文：}

\begin{publications}

%\item
%XXX, XXX, \textbf{XX}, XXX. XXXXXXXX[J]. 中国科学技术大学学报, 200X, xx(xx):xxxx-xxxx.
%
%\item
%XXX, XXX, \textbf{XX}, XXX. XXXXXXXX[J]. 中国科学技术大学学报, 200X, xx(xx):xxxx-xxxx.
%
%\item
%XXX, XXX, \textbf{XX}, XXX. XXXXXXXX[J]. 中国科学技术大学学报, 200X, xx(xx):xxxx-xxxx.

\item N. Y. Xu, J. Zhu, \underline{D. W. Lu}, X. Y. Zhou, X. H. Peng and J. F. Du. Quantum factorization of 143 on a dipolar-coupling NMR system. Phys. Rev. Lett., 2012, 108:130501.

\item Z. K. Li, M. H. Yung, H. W. Chen, \underline{D. W. Lu}, J. D. Whitfield, X. H. Peng, A. Aspuru-Guzik and J. F. Du. Solving quantum ground-state problems with nuclear magnetic resonance.
Scientific Reports, 2011, 1:88.

\item \underline{D. W. Lu}, N. Y. Xu, R. X. Xu, H. W. Chen, J. B. Gong, X. H. Peng, and J. F. Du.
Simulation of chemical isomerization reaction dynamics on a NMR quantum simulator.
Phys. Rev. Lett., 2011, 107:020501.

\item H. W. Chen, \underline{D. W. Lu}, B. Chong, G. Qin, X. Y. Zhou, X. H. Peng, and J. F. Du.
Experimental demonstration of probabilistic quantum cloning.
Phys. Rev. Lett., 2011, 106:180404.

\item J. F. Du, C. Lei, G. Qin, \underline{D. W. Lu}, and X. H. Peng. Search via quantum walk. Search Algorithms and Applications, Nashat Mansour (Ed.), InTech,  Available from: http://www.intechopen.com/articles/show/title/search-via-quantum-walk, 2011.

\item \underline{D. W. Lu}, J. Zhu, P. Zhou, X. H. Peng, Y. H. Yu, S. M. Zhang, Q. Chen, and J. F. Du. Experimental implementation of a quantum random-walk search algorithm using strongly dipolar coupled spins. Phys. Rev. A, 2010, 81:022308.

 \item J. F. Du, N. Y. Xu, X. H. Peng, P. F. Wang, S. F. Wu, and \underline{D. W. Lu}.
NMR implementation of a molecular hydrogen quantum simulation with adiabatic state preparation.
Phys. Rev. Lett., 2010, 104:030502.

\item C. L. Ren, \underline{D. W. Lu}, X. H. Peng, M. J. Shi, and J. F. Du, Experimentally simulating the violation of Bell-type inequalities for generalized GHZ states. Phys. Lett. A, 2009, 373:4222.


\end{publications}

\vskip 1cm

\textbf{待发表论文：}

\begin{publications}

\item \underline{D. W. Lu}, N. Y. Xu, B. R. Xu, Z. K. Li, H. W. Chen, X. H. Peng, R. X. Xu and J. F. Du. Experimental study of the quantum
simulation towards quantum chemistry
with an NMR simulator.
Invited by Phil. Trans. R. Soc. A, accepted.

\item \underline{D. W. Lu}, B. R. Xu, N. Y. Xu, Z. K. Li, H. W. Chen, X. H. Peng, R. X. Xu and J. F. Du. Quantum chemistry simulation on quantum computers: Theories
and Experiments. Invited by Phys. Chem. Chem. Phys. Perspective, accepted.


\end{publications} 